\documentclass[a4paper,10.5pt]{article}  % Increased font size to 11pt
\usepackage[margin=0.3in]{geometry}  % Increased margin to 0.5in for balance
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{parskip}
\usepackage{array}
\setlength{\parskip}{0.3 em}  % Slightly increased space between sections
\setlength{\tabcolsep}{0.5 em}  % Adjusted table padding
\pagestyle{empty}

\title{}
\author{}
\date{}

\renewcommand{\maketitle}{
  \begin{center}
    {\LARGE \textbf{Mohammed Arfa}\par}
  \end{center}
}

\begin{document}
\maketitle

\begin{center}
    \begin{tabular}{ccc}
        \faPhone: +91-9241681626 & \faEnvelope: \href{mailto:thearfa99@gmail.com}{\underline{thearfa99@gmail.com}} & \faLinkedinSquare: \href{https://www.linkedin.com/in/mohammed-arfa/}{\underline{Mohammed Arfa}}
    \end{tabular}
    \vspace{0.4em}
    \begin{center}
        Bengaluru, India
    \end{center}
\end{center}

I am a Computer Science student passionate about leveraging technology to solve real-world problems, proficient in multiple programming languages. Eager to contribute to innovative projects and drive impactful solutions in the tech industry.

\section*{Education}
\vspace{-.3em}
\hrule
\vspace{0.4em}
\begin{itemize}
    \item \textbf{PES University} \hfill \textbf{2022 - Present} \\
          Bachelor of Technology, Computer Science and Engineering \hfill Bengaluru, India
    \item \textbf{The Samhita Academy} \hfill \textbf{2011 - 2022} \\
          CBSE 1st Grade - 12th Grade [Physics, Chemistry, Mathematics and Computer Science] \hfill Bengaluru, India
\end{itemize}

\section*{Experience}
\vspace{-.3em}
\hrule
\vspace{0.4em}
\begin{itemize}
    \item \textbf{Codincity Digital Technologies} \hfill \textbf{July 2024 - August 2024} \vspace{0.3em} \\ 
    Summer Intern - \textbf{React, Node.js, Express, MongoDB Atlas and Tailwind CSS.} \vspace{0.3em} \hfill Bengaluru, India \\
    Developed a project management tool using modern web technologies and following industry best practices. Mod- eled after Jira and Trello, the tool featured task management, user authentication, real-time updates, and automated notifications. This experience sharpened my skills in full-stack development, API integration, and UI design.
          
    \item \vspace{0.3em} \textbf{Destination Designs Private Limited} \hfill \textbf{September 2023 - January 2024} \vspace{0.3em} \\
          Project Intern - \textbf{Next.js, React, MongoDB, Node.js, AWS} \hfill Bengaluru, India \\ \textbf{\href{https://www.destinationdesigns.net.in/}
          {\underline{www.destinationdesigns.net.in}}}  \vspace{0.3em} \\ Collaborated with a team to develop and deploy a professional website for an architectural design client. 
	      \begin{itemize}
		      \item \textbf{Custom Image Optimization Pipeline}: Developed an advanced image optimization pipeline that reduced load times, enhanced scalability, and lowered operational costs.
		      \item \textbf{React and Next.js}: Created a dynamic and responsive user interface to display architecture projects using React, and transitioned database utilities from Express to Next.js Serverless functions, boosting performance and scalability.
	      \end{itemize}
    \item \vspace{0.3em} \textbf{PESU I/O} \hfill \textbf{August 2023 - Present} \\ 
    Deputy Manager \hfill Bengaluru, India \vspace{0.3em} \\
    PESU I/O is PES University’s innovative peer-to-peer learning platform, I assist in developing and delivering diverse educational courses. My role includes collaborating with Subject Matter Experts and facilitating interactive forums and project collaborations, enhancing students’ technical and professional skills.

\end{itemize}

\section*{Programming Skills}
\vspace{-.3em}
\hrule
\vspace{0.4em}

\textbf{Languages}: Python, C, C++, Go, JavaScript, SQL \vspace{0.3em} \\
\textbf{Technologies}: Git, GitHub, MERN Stack, Next.js, AWS, Raylib, HTML5, Tailwind CSS, Postman API, OpenCV
\vspace{-.3em}

\section*{Projects}
\vspace{-.3em}
\hrule
\vspace{0.4em}

\begin{itemize}
    \item \textbf{\href{https://github.com/thearfa99/mern}{\underline{ListMe}}}: A full-stack To-Do List application with user authentication, task management, and automated email notifications using \textbf{React, Node.js, Express and MongoDB Atlas.} Implements \textbf{JWT-secured API endpoints} and \textbf{Postmark} for mailing services.
    \item \textbf{\href{https://github.com/thearfa99/huft}{\underline{Huffman Coding Visualizer}}}: Implements Huffman Coding for lossless data compression in \textbf{C}, with a visual represen- tation of the Huffman Tree using \textbf{Raylib}. It demonstrates encoding processes through clear visual feedback, enhancing understanding of algorithmic efficiency.
    \item \textbf{\href{https://github.com/thearfa99/tureet}{\underline{Target}}}: A \textbf{computer vision} project that implements a face tracking and locking system using \textbf{OpenCV} for face detection and an \textbf{Arduino} for controlling servo motors. The system consists of three main components: Arduino code for servo control, a \textbf{Python} script for face tracking, and a manual control interface using \textbf{Tkinter}.
    \item \textbf{\href{https://github.com/thearfa99/ShopSmart}{\underline{ShopSmart}}}: A shopping list application implemented using a \textbf{Go Microservice}. The project demonstrates various aspects of Go programming, including its concurrency model, standard libraries, and best practices for structuring Go applications.
\end{itemize}

\section*{Certifications}
\vspace{-.3em}
\hrule
\vspace{0.4em}
\begin{itemize}
    \item \textbf{\href{https://www.hackerrank.com/certificates/0546eb7d14c4}{\underline{HackerRank - Problem Solving (Intermediate) Certificate}}}: Covers Data Structures (HashMaps, Stacks, Queues) and Algorithms (Optimal Solutions).
\end{itemize}

\end{document}
